---
title: "Creating constraints file in TestDesign package"
author: Sangdon Lim
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating constraints file in TestDesign package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This document explains how to create a constraint file. In test assembly, practitioners often want to select the items that satify various types of constraints.

## Structure

As of *TestDesign* version 0.2, constraints can be read in from a `.csv` file. The file is expected to be in the following structure:

```{r, eval = F}
CONSTRAINT,TYPE,WHAT,CONDITION,LB,UB,ONOFF
1,Number,Item,,30,30,
2,Number,Item,LEVEL == 3,10,10,
3,Number,Item,LEVEL == 4,10,10,
4,Number,Item,LEVEL == 5,10,10,
5,Number,Item,STANDARD == 1,17,20,
```

The constraint file should have 7 columns, named as `CONSTRAINT`, `TYPE`, `WHAT`, `CONDITION`, `LB`, `UB`, `ONOFF` on the first row of the file.

Beginning from the second row, each row should have the corresponding values for the 6 columns.

A convenient way to creating a `.csv` file is to use a spreadsheet application (e.g. Excel), work on the contents from there, and then saving it as a `.csv` file.

### CONSTRAINT

This column serves as indices for the constraints. A single numeric value should be put into this column, ascending by 1 per row.

### TYPE

This column specifies the type of constraint. The following values are expected: `Number`, `Order`, `Enemy`, `Include`, `Exclude`, `AllorNone`.

* `Number` specifies the constraint to be applied to the number of selected items (if `WHAT` column is `Item`), or to the number of selected item sets (if `WHAT` column is `Stimulus`). For example, the following row tells the solver to select a total of 30 items.

```{r, eval = F}
1,Number,Item,,30,30
```

* `Order` specifies the selection to be made in ascending order. The following row tells the solver to select the items in ascending `LEVEL`, based on the supplied item attributes.

```{r, eval = F}
32,Order,Item,LEVEL,,
```

* `Enemy` specifies the items (or item sets) matching the condition to be treated as enemy items. To tell the solver to select at most one of the two items:

```{r, eval = F}
33,Enemy,Item,"ID %in% c(""SC00001"", ""SC00002"")",,
```

* `Include` specifies the items matching the condition to be included in selection. For example, the following row tells the solver to include the two items `SC00003` and `SC00004`:

```{r, eval = F}
34,Include,Item,"ID %in% c(""SC00003"", ""SC00004"")",,
```

* `Exclude` specifies the items matching the condition to be excluded in selection. The following row tells the solver to exclude the items satisfying `PTBIS < 0.15`, based on the supplied item attributes.

```{r, eval = F}
35,Exclude,Item,PTBIS < 0.15,,
```

* `AllorNone` specifies the items matching the condition to be either all included or all excluded. To tell the solver to either select the items `SC00005` and `SC00006` at the same time or exclude them at the same time:

```{r, eval = F}
36,AllOrNone,Item,"ID %in% c(""SC00005"", ""SC00006"")",,
```

### WHAT

This column specifies where the constraint is applied. The expected values are `Item` or `Stimulus`.

### CONDITION

This column specifies the condition of the constraint. R expressions returning logical values (`TRUE` or `FALSE`) is expected. The variables supplied in item attributes can be used in the expression as variable names.

Some examples are:

* `"STANDARD %in% c(2, 4)"` tells the solver to select when `STANDARD` is either 2 or 4.
* `"STANDARD %in% c(2, 4) & DOK >= 3"` tells the solver to select when `STANDARD` is either 2 or 4, and also `DOK` is at least 3.
* `!is.na(FACIT)` tells the solver to select when `FACIT` is not empty.
* Leave it empty to not specify any condition. This is useful in constraining the total number of items.

Also, `Per Stimulus` can be used to specify the number of items to select in each stimulus. For example, the following row tells the solver to select 4 to 6 items per stimulus:

```{r, eval = F}
3,Number,Item,Per Stimulus,4,6,
```

### LB and UB

These two columns specify the lower and upper bounds on the number of selected items. These columns should be specified when `TYPE` is `Number`, and should be left empty otherwise.

Some example rows are provided.

* To select a total of 12 items:

```{r, eval = F}
1,Number,Item,,12,12
```

* To select 15 to 30 items satisfying `DOK >= 2`:

```{r, eval = F}
17,Number,Item,DOK >= 2,15,30,
```

### ONOFF

This column can be used to turn off a constraint from being applied. The following row specifies the order constraint to be not applied.

```{r, eval = F}
18,Order,Passage,CONTENT,,,OFF
```

